---
title: "Simulated data"
output: html_notebook
---

```{r}
library(EpiEstim)
library(caTools)
library(tidyverse)
files.sources = list.files(".")
files.sources <- files.sources[!str_detect(files.sources, "vignette")]
files.sources <- files.sources[!str_detect(files.sources, "data")]
files.sources <- files.sources[!str_detect(files.sources, "plots")]

for (i in 1:length(files.sources)) {
  source(paste0(c(files.sources[i]), collapse = ''))
}
```

# 1. Victoria
```{r}
df <- read.csv("../../data/covid/VIC.csv")
I <- df$Incidence_Number
I_imp <- df$Imported_Cases
eps <- 1.0
gen = read.csv('../../data/raw/covid_serial_interval.csv')
```

Create total infectiousness: cut-off w at 14 days. Also assume cases are zero before t = 0
```{r}
n_prev_cases <- 14
w <- gen$w[1:n_prev_cases]
w <- w / sum(w)
lambda <- vector(length = length(I))

I_prev = rep(0, n_prev_cases)
I <- c(I_prev, I)
I_imp <- c(I_prev, I_imp)

for(i in seq_along(lambda)) {
  I_past <- rev(I[i:(i + n_prev_cases - 1)] + eps * I_imp[i:(i + n_prev_cases - 1)])
  lambda[i] <- sum(w * I_past)
}
lambda <- c(rep(0, n_prev_cases), lambda)
```

Priors
```{r}
Rprior = c(1, 2); a = 0.05
```

```{r}
# Setup grid and noise parameters
Rmin = 0.01; Rmax = 10; eta = 0.1

# Uniform prior over grid of size m
m = 1000; pR0 = (1/m)*rep(1, m)
# Delimited grid defining space of R
Rgrid = seq(Rmin, Rmax, length.out = m)

# Time series lengths
start_day <- 2
nflu = nrow(df) - start_day
tflu = n_prev_cases + df$Time+ start_day
tflu = tflu[1:(length(tflu) - start_day)]
```

Estimate
```{r}
Rfilt_flu = epiFilter(Rgrid, m, eta, pR0, nflu, lambda[tflu], I[tflu], a)
Rsmooth_flu = epiSmoother(Rgrid, m, Rfilt_flu[[4]], Rfilt_flu[[5]], nflu, Rfilt_flu[[6]], a)
```

Export R estimates
```{r}
results <- tibble(day=df$Time[start_day:(nflu + 1)],
       R_filt=Rfilt_flu[[3]],
       R_filt_lower_bound=Rfilt_flu[[2]][1,],
       R_filt_upper_bound=Rfilt_flu[[2]][2,],
       R_smooth=Rsmooth_flu[[3]],
       R_smooth_lower_bound=Rsmooth_flu[[2]][1,],
       R_smooth_upper_bound=Rsmooth_flu[[2]][2,])
write.table(results, "../../data/covid/results/VIC_R.csv",
            row.names = FALSE, sep = ",")

```



# 2. Queensland
```{r}
df <- read.csv("../../data/covid/QLD.csv")
I <- df$Incidence_Number
I_imp <- df$Imported_Cases
eps <- 1.0
gen = read.csv('../../data/raw/covid_serial_interval.csv')
```

Create total infectiousness: cut-off w at 20 days. Also assume cases are zero before t = 0
```{r}
n_prev_cases <- 14
w <- gen$w[1:n_prev_cases]
w <- w / sum(w)
lambda <- vector(length = length(I))

I_prev = rep(0, n_prev_cases)
I <- c(I_prev, I)
I_imp <- c(I_prev, I_imp)

for(i in seq_along(lambda)) {
  I_past <- rev(I[i:(i + n_prev_cases - 1)] + eps * I_imp[i:(i + n_prev_cases - 1)])
  lambda[i] <- sum(w * I_past)
}
lambda <- c(rep(0, n_prev_cases), lambda)
```

Priors
```{r}
Rprior = c(1, 2); a = 0.05
```

```{r}
# Setup grid and noise parameters
Rmin = 0.01; Rmax = 10; eta = 0.1

# Uniform prior over grid of size m
m = 1000; pR0 = (1/m)*rep(1, m)
# Delimited grid defining space of R
Rgrid = seq(Rmin, Rmax, length.out = m)

# Time series lengths
start_day <- 2
nflu = nrow(df) - start_day
tflu = n_prev_cases + df$Time+ start_day
tflu = tflu[1:(length(tflu) - start_day)]
```

Estimate
```{r}
Rfilt_flu = epiFilter(Rgrid, m, eta, pR0, nflu, lambda[tflu], I[tflu], a)
Rsmooth_flu = epiSmoother(Rgrid, m, Rfilt_flu[[4]], Rfilt_flu[[5]], nflu, Rfilt_flu[[6]], a)
```

Export R estimates
```{r}
results <- tibble(day=df$Time[start_day:(nflu + 1)],
       R_filt=Rfilt_flu[[3]],
       R_filt_lower_bound=Rfilt_flu[[2]][1,],
       R_filt_upper_bound=Rfilt_flu[[2]][2,],
       R_smooth=Rsmooth_flu[[3]],
       R_smooth_lower_bound=Rsmooth_flu[[2]][1,],
       R_smooth_upper_bound=Rsmooth_flu[[2]][2,])
write.table(results, "../../data/covid/results/QLD_R.csv",
            row.names = FALSE, sep = ",")

```





# 3. Hong Kong
```{r}
df <- read.csv("../../data/covid/HK.csv")
I <- df$Incidence_Number
I_imp <- df$Imported_Cases
eps <- 0.2
gen = read.csv('../../data/raw/covid_serial_interval.csv')
```

Create total infectiousness: cut-off w at 20 days. Also assume cases are zero before t = 0
```{r}
n_prev_cases <- 14
w <- gen$w[1:n_prev_cases]
w <- w / sum(w)
lambda <- vector(length = length(I))

I_prev = rep(0, n_prev_cases)
I <- c(I_prev, I)
I_imp <- c(I_prev, I_imp)

for(i in seq_along(lambda)) {
  I_past <- rev(I[i:(i + n_prev_cases - 1)] + eps * I_imp[i:(i + n_prev_cases - 1)])
  lambda[i] <- sum(w * I_past)
}
lambda <- c(rep(0, n_prev_cases), lambda)
```

Priors
```{r}
Rprior = c(1, 2); a = 0.05
```

```{r}
# Setup grid and noise parameters
Rmin = 0.01; Rmax = 10; eta = 0.1

# Uniform prior over grid of size m
m = 1000; pR0 = (1/m)*rep(1, m)
# Delimited grid defining space of R
Rgrid = seq(Rmin, Rmax, length.out = m)

# Time series lengths
start_day <- 2
nflu = nrow(df) - start_day
tflu = n_prev_cases + df$Time+ start_day
tflu = tflu[1:(length(tflu) - start_day)]
```

Estimate
```{r}
Rfilt_flu = epiFilter(Rgrid, m, eta, pR0, nflu, lambda[tflu], I[tflu], a)
Rsmooth_flu = epiSmoother(Rgrid, m, Rfilt_flu[[4]], Rfilt_flu[[5]], nflu, Rfilt_flu[[6]], a)
```

Export R estimates
```{r}
results <- tibble(day=df$Time[start_day:(nflu + 1)],
       R_filt=Rfilt_flu[[3]],
       R_filt_lower_bound=Rfilt_flu[[2]][1,],
       R_filt_upper_bound=Rfilt_flu[[2]][2,],
       R_smooth=Rsmooth_flu[[3]],
       R_smooth_lower_bound=Rsmooth_flu[[2]][1,],
       R_smooth_upper_bound=Rsmooth_flu[[2]][2,])
write.table(results, "../../data/covid/results/HK_R.csv",
            row.names = FALSE, sep = ",")

```


