---
title: "Simulated data"
output: html_notebook
---

```{r}
library(EpiEstim)
library(caTools)
library(tidyverse)
files.sources = list.files(".")
files.sources <- files.sources[!str_detect(files.sources, "vignette")]
files.sources <- files.sources[!str_detect(files.sources, "data")]
files.sources <- files.sources[!str_detect(files.sources, "plots")]

for (i in 1:length(files.sources)) {
  source(paste0(c(files.sources[i]), collapse = ''))
}
```

# 1. Covid
## Synthetic drop-off
```{r}
df <- read.csv("../../data/synthetic/synthetic1_dropoff.csv")
I <- df$cases
gen = read.csv('../../data/raw/covid_serial_interval.csv')
```

Create total infectiousness: cut-off w at 20 days. Also assume cases are zero before t = 0
```{r}
n_prev_cases <- 20
w <- gen$w[1:n_prev_cases]
w <- w / sum(w)
lambda <- vector(length = length(I))

I_prev = rep(0, n_prev_cases)
I_prev[length(I_prev)] = 5
I_prev[length(I_prev)-1] = 5
I_prev[length(I_prev)-2] = 5
I <- c(I_prev, I)

for(i in seq_along(lambda)) {
  I_past <- rev(I[i:(i + n_prev_cases - 1)])
  lambda[i] <- sum(w * I_past)
}
lambda <- c(rep(0, n_prev_cases), lambda)
```

Priors
```{r}
Rprior = c(1, 2); a = 0.05
```

```{r}
# Setup grid and noise parameters
Rmin = 0.01; Rmax = 10; eta = 0.1

# Uniform prior over grid of size m
m = 1000; pR0 = (1/m)*rep(1, m)
# Delimited grid defining space of R
Rgrid = seq(Rmin, Rmax, length.out = m)

# Time series lengths
nflu = nrow(df)
tflu = n_prev_cases + df$day
```

Estimate
```{r}
Rfilt_flu = epiFilter(Rgrid, m, eta, pR0, nflu, lambda[tflu], I[tflu], a)
Rsmooth_flu = epiSmoother(Rgrid, m, Rfilt_flu[[4]], Rfilt_flu[[5]], nflu, Rfilt_flu[[6]], a)
```

Export R estimates
```{r}
results <- tibble(day=df$day,
       R_filt=Rfilt_flu[[3]],
       R_filt_lower_bound=Rfilt_flu[[2]][1,],
       R_filt_upper_bound=Rfilt_flu[[2]][2,],
       R_smooth=Rsmooth_flu[[3]],
       R_smooth_lower_bound=Rsmooth_flu[[2]][1,],
       R_smooth_upper_bound=Rsmooth_flu[[2]][2,])
write.table(results, "../../data/synthetic/results/synthetic_1_R.csv",
            row.names = FALSE, sep = ",")

```

## Slow drop-off: COVID
```{r}
df <- read.csv("../../data/synthetic/synthetic3_slowdropoff.csv")
I <- df$cases
```

Create total infectiousness: cut-off w at 20 days. Also assume cases are zero before t = 0
```{r}
n_prev_cases <- 20
w <- gen$w[1:n_prev_cases]
w <- w / sum(w)
lambda <- vector(length = length(I))

I_prev = rep(0, n_prev_cases)
I_prev[length(I_prev)] = 5
I_prev[length(I_prev)-1] = 5
I_prev[length(I_prev)-2] = 5
I <- c(I_prev, I)

for(i in seq_along(lambda)) {
  I_past <- rev(I[i:(i + n_prev_cases - 1)])
  lambda[i] <- sum(w * I_past)
}
lambda <- c(rep(0, n_prev_cases), lambda)
```

Priors
```{r}
Rprior = c(1, 2); a = 0.05
```

```{r}
# Setup grid and noise parameters
Rmin = 0.01; Rmax = 10; eta = 0.1

# Uniform prior over grid of size m
m = 1000; pR0 = (1/m)*rep(1, m)
# Delimited grid defining space of R
Rgrid = seq(Rmin, Rmax, length.out = m)

# Time series lengths
nflu = nrow(df)
tflu = n_prev_cases + df$day
```

Estimate
```{r}
Rfilt_flu = epiFilter(Rgrid, m, eta, pR0, nflu, lambda[tflu], I[tflu], a)
Rsmooth_flu = epiSmoother(Rgrid, m, Rfilt_flu[[4]], Rfilt_flu[[5]], nflu, Rfilt_flu[[6]], a)
```

Export R estimates
```{r}
results <- tibble(day=df$day,
       R_filt=Rfilt_flu[[3]],
       R_filt_lower_bound=Rfilt_flu[[2]][1,],
       R_filt_upper_bound=Rfilt_flu[[2]][2,],
       R_smooth=Rsmooth_flu[[3]],
       R_smooth_lower_bound=Rsmooth_flu[[2]][1,],
       R_smooth_upper_bound=Rsmooth_flu[[2]][2,])
write.table(results, "../../data/synthetic/results/synthetic_3_R.csv",
            row.names = FALSE, sep = ",")
```

## Drop-off then resurgence: Ebola
```{r}
df <- read.csv("../../data/synthetic/synthetic2_resurgence.csv")
I <- df$cases
gen = read.csv('../../data/synthetic/ebola_serial_interval.csv', header = F)
```

Create total infectiousness: cut-off w at 50 days. Also assume cases are zero before t = 0 (just to make total infectiousness easier to calculate).
```{r}
n_prev_cases <- 50
w <- gen$V1[1:n_prev_cases]
w <- w / sum(w)
lambda <- vector(length = length(I))

I_prev = rep(5, n_prev_cases)
I <- c(I_prev, I)

for(i in seq_along(lambda)) {
  I_past <- rev(I[i:(i + n_prev_cases - 1)])
  lambda[i] <- sum(w * I_past)
}
lambda <- c(rep(0, n_prev_cases), lambda)
```

Priors
```{r}
Rprior = c(1, 2); a = 0.05
```

```{r}
# Setup grid and noise parameters
Rmin = 0.01; Rmax = 10; eta = 0.1

# Uniform prior over grid of size m
m = 1000; pR0 = (1/m)*rep(1, m)
# Delimited grid defining space of R
Rgrid = seq(Rmin, Rmax, length.out = m)

# Time series lengths: start on day after first day as otherwise lambda is zero on first two days causing NAs
start_day <- 2
nflu = nrow(df) - start_day
tflu = n_prev_cases + df$day+ start_day
tflu = tflu[1:(length(tflu) - start_day)]
```

Estimate
```{r}
Rfilt_flu = epiFilter(Rgrid, m, eta, pR0, nflu, lambda[tflu], I[tflu], a)
Rsmooth_flu = epiSmoother(Rgrid, m, Rfilt_flu[[4]], Rfilt_flu[[5]], nflu, Rfilt_flu[[6]], a)
```

Export R estimates
```{r}
results <- tibble(day=df$day[start_day:(nflu + 1)],
       R_filt=Rfilt_flu[[3]],
       R_filt_lower_bound=Rfilt_flu[[2]][1,],
       R_filt_upper_bound=Rfilt_flu[[2]][2,],
       R_smooth=Rsmooth_flu[[3]],
       R_smooth_lower_bound=Rsmooth_flu[[2]][1,],
       R_smooth_upper_bound=Rsmooth_flu[[2]][2,])
write.table(results, "../../data/synthetic/results/synthetic_2_R.csv",
            row.names = FALSE, sep = ",")
```